Blue Hunters: Bluetooth RSSI Locator Robots

### 2018-02-06 article/article.tex
Basic restructuring + delisting

@@

\subsection{Hardware}

@@

@@

\paragraph{Servos}

@@

\paragraph{Gradient descent}

@@

There are many potential avenues for improvements or further
development:

\begin{itemize}
\tightlist
\item
  \emph{Communication between the two robots}. While Bluetooth may not offer good distance measurement via RSSI, it can be used for reliable  communication between modules.
  It would be straightforward for one hunting robot to inform the other whether it believes it is approaching the beacon or not.
  In the simplest case, a robot that is approaching, or already at, the beacon can provide a second point of reference for a currently hunting robot.
\item
  \emph{More complete usage of IMU}. Additional usage of the accelerometer and gyroscope, coupled with feedback from the servos, would allow the robots to maintain a dead-reckoning position estimate.
  This, paired with inter-swarm communication, would make for a much more sophisticated and likely much more efficient system.
  (Of course, this does not resolve the shallow gradients problem -- but it would allow the approach to the beacon to be much faster.)
\end{itemize}

>>>>

% TODO: motivation, RSSI, fake chips

@@

\subsection{Design}

@@

% Possible subsections?
% - building robot
% - signal detection
% - navigation

@@

% \paragraph{Servos}

@@

% \paragraph{Gradient descent}

@@

There are many potential avenues for improvements or further
development.

Firstly, \emph{Communication between the two robots}: while Bluetooth may not offer good distance measurement via RSSI, it can be used for reliable  communication between modules.
It would be straightforward for one hunting robot to inform the other whether it believes it is approaching the beacon or not.
In the simplest case, a robot that is approaching, or already at, the beacon can provide a second point of reference for a currently hunting robot.

Also, \emph{More complete usage of IMU}: additional usage of the accelerometer and gyroscope, coupled with feedback from the servos, would allow the robots to maintain a dead-reckoning position estimate.
This, paired with inter-swarm communication, would make for a much more sophisticated and likely much more efficient system.
(Of course, this does not resolve the shallow gradients problem -- but it would allow the approach to the beacon to be much faster.)
